\section*{Message from the General Chair}\vspace{2em}
\setheaders%
    {Message from the General Chair}%
    {Message from the General Chair}
\thispagestyle{emptyheader}
\begin{large}
\setlength{\parskip}{1ex}

\noindent Welcome everyone!

It is my pleasure to welcome you all to Atlanta, Georgia, for the 2013 NAACL Human Language Technologies conference.  This is a great opportunity to reconnect with old friends and make new acquaintances, learn the latest in your own field and become curious about new areas, and also to experience Atlanta's warm southern hospitality.
That hospitality starts with Priscilla Rasmussen! Priscilla thinks about everything that we all take for granted: the registration that just took place, the rooms in which we sit, the refreshments that keep us energized, and the social events that make this conference so fun, and many other details that you would miss if they weren't there. Please introduce yourself and say hi. Priscilla is the backbone of the NAACL organization. Thank you!

This conference started a year ago, when Hal Daumé III and Katrin Kirchhoff graciously agreed to be program co-chairs. It is no exaggeration to say how much their dedication has shaped this conference and how grateful I am for their initiative and hard work. Thank you Hal and Katrin, especially for all the fun discussion that made the work light and the year go by fast!  This conference could not have happened with you.

Thanks go to the entire organizing committee. As I am writing this to be included in the proceedings, I am grateful for the fantastic detailed and proactive work by Colin Cherry and Matt Post, the publications chairs.  The tutorials chairs, Katrin Erk and Jimmy Lin, selected, and solicited, 6 tutorials to present in depth material on some of the diverse topics represented in our community. Chris Dyer and Derrick Higgins considered which projects shine best when shown as a demonstration.  The workshops chairs for NAACL, Sujith Ravi and Luke Zettlemoyer, worked jointly with ACL and EMNLP to select the workshops to be held at NAACL. They also worked with ICML 2013 to co-host workshops that bridge the two communities, in addition to the Joint NAACL/ICML symposium.

Posters from the student research workshop are part of the poster and demonstrations session on Monday night. This is a great opportunity for the students to be recognized in the community and to benefit from lively discussion of their presentations (attendees take note!) Annie Louis and Richard Socher are the student research workshop chairs, and Julia Hockenmaier and Eric Ringger generously share their wisdom as the faculty advisors.  The student research workshop itself will be held on the first day of workshops.
There are so many people who contribute their time to the behind-the-scenes organization of the conference, without which the conference cannot take place. Asking for money is probably not a natural fit for anyone, but Chris Brew worked on local sponsorship, and Dan Bikel and Patrick Pantel worked to obtain sponsorship across the ACL conferences this year - thank you!  Jacob Eisenstein had the more fun role of distributing money as the student volunteer coordinator, and we thank all of the student volunteers who will be helping to run a smooth conference.  Kristy Boyer kept the communication ``short and tweet'' using a variety of social media (and old-fashioned media too).
An important part of the behind-the-scenes efforts that enable a conference like NAACL to come together are the sponsors. We thank all of the sponsors for the contributions to the conference , both for the general funding made available as well as the specific programs that are funded through sponsorship.  You can read more about these sponsors in our conference handbook.

This year there are several initiatives, and if successful, we hope  they’ll be part of NAACL conferences in the future. One is to make the proceedings available prior to the conference; we hope you will benefit from the extra time to read the papers beforehand.  Another is for tutorials and all oral presentations to be recorded on video and made available post-conference. We are also delighted to host presentations, in both oral and poster formats, from the new Transactions of the ACL journal, to enhance the impact these will already have as journal publications. Finally, Matt Post is creating a new digital form of conference handbook to go with our digital age; thanks also go to  Alex Clemmer who  has prepared the paper copy that you may be reading right now.  We hope you use the \#NAACL2013 tag when you are tweeting about the conference or papers at the conference; together, we'll be creating a new social media corpus to explore.

Once again, we are pleased to be co-located with *SEM conference, and the SemEval workshop. We are lucky to have ICML 2013 organized  so  close  in time and place.  Several  researchers who span the two communities have reconvened the Joint NAACL/ICML symposium on June  15, 2013. In addition, two workshops that address areas of interest to both NAACL and ICML members have been organized on June 16th, as part of the ICML conference.

NAACL 2013 has given me a great appreciation for the volunteering that is part of our culture. Besides the organizing committee itself, we are guided by the NAACL executive board, who think about questions with a multi-year perspective. I also want to recognize the members who first initiated and now maintain the ACL Anthology, where all of our published work will be available to all in perpetuity, a fabulous contribution and one that distinguishes our academic community.

Have a fun conference!

\vspace{.2in}
Lucy Vanderwende, Microsoft Research \\
\indent NAACL HLT 2013 General Chair
\end{large}
